The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-27 paper.Rmd
update

```{r simulation_1, echo=FALSE, warning=FALSE, message=FALSE}
#SLOW COMPUTATION.. FOR FAST COMPUTE SEE LINES 11, 20, 65, & 79 
# Load required libraries
if (!require("reshape2")) install.packages("reshape2")
if (!require("ggplot2")) install.packages("ggplot2")
library(reshape2)
library(ggplot2)
# Define reaction rates
c1 <- (37 / 1e6) * 10             # Formation of CPD
c2 <- (2 / 1e6) * 10              # Formation of 64-PP
c3 <- (1 - (37 + 2) / 1e6) * 10   # No dimerization occurs// REMOVE THIS LINE FOR FAST COMPUTE

>>>>

```{r simulation_1, echo=FALSE, warning=FALSE, message=FALSE}
#SLOW COMPUTATION.. FOR FAST COMPUTE MAKE ADJUSTMENTS AS NEEDED
# Load required libraries
if (!require("reshape2")) install.packages("reshape2")
if (!require("ggplot2")) install.packages("ggplot2")
library(reshape2)
library(ggplot2)
# Define reaction rates
c1 <- (37 / 1e6) * 10             # Formation of CPD
c2 <- (2 / 1e6) * 10              # Formation of 64-PP
c3 <- (1 - (37 + 2) / 1e6) * 10   # No dimerization occurs// REMOVE THIS LINE FOR FAST COMPUTE
